Multi-level modelling with Openflexo/FML - A contribution to the \mpc

### 2021-05-28 3-Introduction.tex
replace eg by macro

This strict approach shows its limitations when modeling complex domains requiring more than one level of specialization, e.g., to adapt the model to application sub domains. Indeed, the two-level approach fails to acknowledge and support: 1) the existence of different forms of classification and/or instantiation (e.g., ontological vs linguistic); and 2) the duality type-object for model elements. Therefore, while it may still be used for the aforementioned complex modeling tasks, the strict approach entails the introduction of accidental complexity in both the modeling process and the resulting modeling artefacts.

>>>>

This strict approach shows its limitations when modeling complex domains requiring more than one level of specialization, \eg to adapt the model to application sub domains. Indeed, the two-level approach fails to acknowledge and support: 1) the existence of different forms of classification and/or instantiation (\eg ontological vs linguistic); and 2) the duality type-object for model elements. Therefore, while it may still be used for the aforementioned complex modeling tasks, the strict approach entails the introduction of accidental complexity in both the modeling process and the resulting modeling artefacts.

### 2021-05-28 8-Discussion.tex
replace eg by macro

As described in section~\ref{subsec:tooling}, our solution is fully tooled with Openflexo.
We use the Openflexo infrastructure to build models and metamodels together, and to provide 
dedicated tooling to edit a Process type, to enact a process and to execute it. Being able to provide a solution and its associated tools quickly and easily is an \textcolor{red}{interesting} feature. 
We could also have taken advantage of the model federation to connect our solution to other tools 
dedicated to process edition and to process execution (\emph{e.g.} a BPMN engine). However we 
already had all the necessary components to provide the aforementioned graphical tools.

>>>>

As described in section~\ref{subsec:tooling}, our solution is fully tooled with Openflexo.
We use the Openflexo infrastructure to build models and metamodels together, and to provide 
dedicated tooling to edit a Process type, to enact a process and to execute it. Being able to provide a solution and its associated tools quickly and easily is an \textcolor{red}{interesting} feature. 
We could also have taken advantage of the model federation to connect our solution to other tools 
dedicated to process edition and to process execution (\eg a BPMN engine). However we 
already had all the necessary components to provide the aforementioned graphical tools.
